Meeting Agenda with Domain Experts

### 2021-01-04 StateOfPractice/Methodology/Meeting Agenda with Domain Experts.tex
modified "Survey for Short List Projects"

After the first round of measurement, we would like to select a short list of
projects (about 5 of them for each domain) and directly ask questions to the
developers.

We would like to do the selection based on the results of the first round
measurement, such as selecting the top 5 ones with the highest scores. However, we
can also include 1 or 2 most recommended ones from you. What do you think of
this selection process?

The survey questions to the developers can be found at
\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Ao-Notes/Questions%20to%20Developers.pdf}{Questions
	to Developers}.

>>>>

After the first round of measurement, we would like to select a short list of
projects (about 5 to 10 of them for each domain) and directly ask questions to the
developers.

Considering the fact that some development teams may ignore our requests for
this interview, We would like to send invitations to all of the teams developing
the software packages in the list. We estimate that there will be a smaller
proportion of them accepting our request. What do you think of
this process?

The survey questions to the developers can be found at
\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Questions%20to%20Developers.pdf}{Questions
	to Developers}.

We also would like to ask the domain experts a modified version of the above
questions. The purpose will be to learn how our domain experts and their
students create software. If we time it right, the interview with the domain
experts is also a chance to do a dry run with our questions.
